---
title: "task3"
output: pdf_document
---
---
title: "MA615 Assignment4 Task Three"
author: "Yuyang Li"
date: "2021/12/8"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F,message = F,echo=F,highlight=F)

library(devtools)
library(rticles)
# Set tnum database and source function
library(tnum)
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")
source("Book2TN-v6A-1.R")
```


```{r, echo=FALSE}

#devtools::install_github("Truenumbers/tnum/tnum",force = TRUE)
#install.packages("textdata")
knitr::opts_chunk$set(fig.width=6, fig.height=4,fig.align = "center") 
pacman::p_load(
  gutenbergr,
  tidytext,
  magrittr,
  textdata,
  dplyr,
  stringr,
  tidyverse,
  tidyr,
  scales,
  reshape2,
  ggplot2,
  tinytex,
  latexpdf,
  sentimentr)

```

```{r, echo=FALSE}
data<- gutenberg_download(4980)
```


## Task three
```{r}
#write.table(data,'Garden.txt',row.names = F) 
#garden <- read.table('Garden.txt',header = TRUE)
```

```{r}
#tnBooksFromLines(garden$text, "Burnett/Garden")
```

```{r}
# Changing my book into tnum
#write.table(data,'Fox.txt',row.names = F) 
fox <- read.table('Fox.txt',header = TRUE)
#tnBooksFromLines(fox$text, "Burgess/Fox")
```





```{r}
# Create tidy book
tidy_fox <- fox %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("chapter", 
                                      ignore_case = TRUE)))) %>% 
  unnest_tokens(word, text) 
```

First of all, I change my book into tnum form, and the content of my tnum database is shown as follow:



Secondly I use 'sentimentr' to get sentiment score group by these scores with section to get the average result. The plot sort the average sentiment score from high to low.
```{r}
# Separate into different columns
query<- tnum.query('Burgess/fox/section# has text',max=5000) %>% tnum.objectsToDf()
query %>% view()
fox_sentence<-query %>% separate(col=subject,
                  into = c("path1", "path2","section","paragraph","sentence"), 
                  sep = "/", 
                  fill = "right") %>% 
  select(section:string.value)
```

```{r}
# Get the number of section, paragraph and sentence
fox_sentence<-fox_sentence %>% 
  mutate_at(c('section','paragraph','sentence'),~str_extract_all(.,"\\d+") %>%
              unlist() %>%
              as.numeric())%>%
  filter(section !=0)
```


```{r}
# Use sentimentr to get sentiment score group by these scores with section to get the average result
library(magrittr)
sentence_out<-fox_sentence %>%
  filter(section !=0)%>% dplyr::mutate(sentence_split = get_sentences(string.value)) %$%
    sentiment_by(sentence_split, list(section))
  

plot(sentence_out)
```


### Compare the analysis result with Task two

Because the scale of scores of two methods are different, so I need to change them into one consistent scale using function, then I get the bar plot for two scores.


```{r}
# Create a new bing with index=chapter
new_bing<-tidy_fox %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al.") %>% 
    count(method, index = chapter, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

# Scale sentiment to keep unit same 
new_bing2<-new_bing %>% 
  mutate(bing_scale=scale(sentiment)) %>% 
  select(method,index,bing_scale)

# Change the name of column two in order to join by section
colnames(new_bing2)[2]='section'

# Scale sentiment to keep unit same 
sentence_out<-sentence_out %>% mutate(sentimentr_scale=scale(ave_sentiment))

# Join two df
sentence_out_2method<-left_join(sentence_out,new_bing2,by='section')%>% select(section,bing_scale,sentimentr_scale)

# Use pivot longer for ggplot
sentence_out_2method_plot<-sentence_out_2method %>% pivot_longer(cols=c('sentimentr_scale','bing_scale'),names_to = 'sentiment')

# Create barplot to compare
sentence_out_2method_plot %>%ggplot(aes(y=value,x=factor(section))) +
  geom_bar(aes(fill=factor(sentiment)),stat='identity',position = "dodge",width = 0.7)+theme_bw()

```

## Extra credit of Task three: character analysis

As I mentioned in Task two, there are two main characters in this book, one is Granny Fox and other is Reddy. So I select them from my book and count their appeared frequency in each chapter. seeing the table I found in most of the chapter Granny appears more than Reddy.

```{r}
# Find the two main characters Granny and Reddy
book_sentence_indi<-fox_sentence %>% mutate(granny=str_match(fox_sentence$string.value,regex('(Granny)'))[,1],
                         reddy=str_match(fox_sentence$string.value,regex('(Reddy)'))[,1])
# Use sentiment_by to get the score
score<-book_sentence_indi %>% dplyr::mutate(sentence_split = get_sentences(string.value))%$%
    sentiment_by(sentence_split) %>% `$`(ave_sentiment)
# Count two characters' time in each chapter
book_sentence_indi$score<-score
re<-book_sentence_indi %>% group_by(section) %>% summarise(granny=sum(granny %>% is.na() %>% `!`()),
                                                       reddy=sum(reddy%>% is.na() %>% `!`()))
knitr::kable(re,'simple')
# use group by to display the result
re2<-book_sentence_indi %>% group_by(section,paragraph) %>% summarise(
  both_appear=sum(granny %>% is.na() %>% `!`() & reddy%>% is.na() %>% `!`() ))
#re2 %>% filter(both_appear>0)
knitr::kable(re2 %>% filter(both_appear>0),'simple')
```
